ISSSV1337 Group 5 Report

### 2022-08-03 Report/Group 5 report.Rmd
Adding Github link.

@@

## Phase 1: How to harvest and analyse the data? {.smaller}

OPX wanted us to harvest the organisations' financial data from the web.
During the first stage of brainstorming, we wanted to find a simple and
automated way to do so.

We discussed creating web scraping code that could collect data across
different websites, but quickly decided that this would be too
difficult, and that it would only work with selected organisations. The next
suggested solution was to create code that could read PDF documents
that OPX downloaded themselves. Our code would analyse and organise the
uploaded data from the PDF documents.

@@

```{r, echo=FALSE, fig.cap="Need caption"}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

# inkluder en med årsregnskapet som pdf her
```

## Phase 2: Exploring solutions {.smaller}

@@

- Financial statements in annual report PDF documents. 
- Web scrape Proff.no for financial statements. 
- Web scrape the Brønnøysund registry.

We divided the task among ourselves to explore whether these solutions
were feasible or not. The first option of using PDF documents still had
the issue of financial statements not always being published as text, as well as their often wildly differing formats. Unfortunately, we quickly found that Proff.no disallows any automated collection of data from their website. The Brønnøysund registry does offer API access to all the financial statements, but we discovered that access currently costs NOK 480,000.

We started to look at workarounds for this problem. It could still be
possible to download Proff.no HTML websites manually for each
organisation. We did receive some XML files from Statistics Norway, but using these is ultimately not a viable solution for OPX.

@@

```{r, echo=FALSE, fig.cap="Need caption", fig.align='center'}
knitr::include_graphics("Images/info_kreft.png")
```

```{r, echo=FALSE, out.width="100%", fig.cap="Need caption"}
knitr::include_graphics("Images/regnskapssti.png")
```

When also discovering that not all organisations publish their financial
statements, and certainly not for every year, we decided to give up on
collecting financial data for OPX, as the task turned out to impossible given current reporting requirements and practices. This is when we moved on to the third
and final stage.

## Phase 3: Scrapping the scraping {.smaller}

@@

We wanted to use web scraping to collect the data, so that we could have
automated the data input process. As described, we explored different
potential solutions. We experimented on coding such that data could have
been imported from XML files. However, once we realised that the available
financial data was of little use, this experimentation stopped.

As we entered the third phase of brainstorming, we still needed some
example data so that we could test our KPI codes. For this, we used the
financial data that OPX had already gathered from different
organizations and organized into useful accounting items.

We copied these financial statements manually into an Excel document.
Perhaps a 'simple' solution, however our code requires OPX to import
both an Excel document themselves into shiny, as well as a HTML document
from Proff.no.

@@

<!--# Fra Visualisations (nedenfor): The plots based on data from Proff.no often demonstrate surprising lacunae, but it difficult to know where they originate -- NGO reporting, Brønnøysund, or Proff.no.-->

<!--Legg inn bilder her-->

<!-- # Legger inn fire grafer som viser manglende data i Proffs årsregnskap-->

>>>>

**Github**: [https://github.com/torbjornso/ISSSV1337group5](https://github.com/torbjornso/ISSSV1337group5)

@@

## Phase 1: How to harvest and analyse the data?

OPX wanted us to harvest the organizations' financial data from the web.
During the first stage of brainstorming, we wanted to find a simple and
automated way to do so.

We discussed creating web scraping code that could collect data across
different websites, but quickly decided that this would be too
difficult, and that it would only work with selected organizations. The
suggested solution was to create code that could read PDF documents
that OPX downloaded themselves. Our code would analyse and organise the
uploaded data from the PDF documents.

@@

```{r, echo=FALSE, fig.cap="Norwegian Cancer Society 2021: The financial report saved as text in the PDF."}
# Illustration some text some pictures in financial statements
knitr::include_graphics("Images/lagret_tekst.png") # Kreftforeningen 2021
```

```{r, echo=FALSE, fig.cap="Rainforest Foundation 2018: The financial report saved as an image in the PDF."}
# Illustration some text some pictures in financial statements
knitr::include_graphics("Images/lagret_bilde.png") # Regnskogfondet 2018
```

## Phase 2: Exploring solutions

@@

- Financial statements in anual report PDF documents. 
- Web scrape Proff.no for financial statements. 
- Web scrape the Brønnøysund registry.

We divided the task among ourselves to explore whether these solutions
were feasible or not. The first option of using PDF documents still had
the issue of financial statements not always being published as text.
Also, we quickly found that Proff.no disallowed web scraping on their
website. The Brønnøysund registry did offer API access to all the financial statements on their website, but we discovered that
access to these data costs about half a million NOK.

We started to look at workarounds for this problem. It would still be
possible to download Proff.no HTML web pages manually for each
organisation. We also received access to some XML files from Statistics Norway, but this would not be a viable solution for OPX in the long term.

@@

```{r, echo=FALSE, fig.cap="Accounting items for the Norwegian Cancer Society 2020 and the Norwegian Diabetes Association 2020, gathered from the Brønnøysund registry.", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/Brns_items1.png")
```

```{r, echo=FALSE, fig.cap="Accounting items for the Norwegian Cancer Society 2020 and the Norwegian Diabetes Association 2020, gathered from OPX.", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/OPX_items1.png")
```

```{r, echo=FALSE, fig.cap="An attempt at marrying the two sets of accounting items.", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/Marriage.png")
```

When we also discovered that not all organisations publish their financial
statements, and certainly not for every year, we decided to give up on
collecting financial data for OPX. This is when we moved on to the third
and final stage.

```{r, echo=FALSE, out.width="100%", fig.cap="The Rainforest Foundation stopped posting financial statement PDFs on their website in 2018."}
# Illustration only published for some years example
knitr::include_graphics("Images/Regnskogfondet_stops2018.png")
```

```{r, echo=FALSE, out.width="50%", fig.align='center', fig.cap="The Norwegian Cancer Society started posting financial statement PDFs on their website in 2019."}
# Illustration only published for some years example
knitr::include_graphics("Images/Kreftforeningen_starts2019.png")
```

## Phase 3: Scrapping the scraping

@@

We wanted to use web scraping to collect the data, so that we could have
automated the data input process. As described, we explored different
potential solutions. We experimented on coding such that data could have
been imported from XML files. However, once we realised that the
financial data was of little use, this experimentation stopped.

As we entered the third phase of brainstorming, we still needed some
example data so that we could test our KPI codes. For this, we used the
financial data that OPX had already gathered from different
organisations and organised into useful accounting items.

We copied these financial statements manually into an Excel document.
Perhaps a 'simple' solution, however our code requires OPX to upload
both an Excel document, as well as a HTML document
from Proff.no, to the dashboard.

```{r, echo=FALSE, out.width="100%", fig.cap="The data format used to upload to the dashboard."}
# Bilde av den "endelige" excel-versjonen som brukes til å laste inn i shiny
knitr::include_graphics("Images/Excel_final.png")
```

@@

Our data was gathered from OPX's own web page, and from Proff.no. As described 
in the previous parts, we wanted to gather data from the annual reports or by 
scraping the Brønnøyund registry or Proff.no, but found this to be impossible. The data used is the one that OPX has gathered themselves directly 
from the organisations. This data was also used to test that our codes in R 
were correct.

We have also used Proff.no to visualise the annual incomes and some KPIs. 
This is data that the organisations have reported themselves to Proff.no. 
Since there are no regulations regarding reporting data for NGOs in Norway, 
the organisations have not been consistent with the data reporting. This may 
explain the lacunae in the presented data (see e.g. figures 9 and 10).
